Think deep for reef resilience

### 2025-08-10 paper/paper_draft.qmd
Quantify average number of low clustered reefs across GCMs

Under all GCMs most reefs are projected to suffer substantial declines in coral cover
relative to 2025 levels. NorESM2-MM and ACCESS-ESM1-5 GCMs convey the most coral cover
maintenance into the future. Differences between low, medium and high reef clusters in cover
timeseries are most notable under these two GCMs [@tbl-cluster-cid;
@fig-gcm-cover-trajectories]. Maintainance of coral cover into the future is linked to the
Equilibrium Climate Sensitivity of the GCM used as levels of future recovery and timespan of
cover maintainance increase as GCM ECS increases [@fig-gcm-cover-trajectories]. Under
high-ECS GCMs (GFDL-CM4, EC-Earth3-Veg and ACCESS-CM2) large declines and lower rates of
recovery in high cover clusters are common compared to lower-ECS GCMs.

>>>>

Under all GCMs many reefs are projected to suffer substantial declines in coral cover
relative to 2025 levels, with an average of 38% of reefs (924 reefs) clustered into the
lowest cover level cluster across GCMs. NorESM2-MM and ACCESS-ESM1-5 GCMs convey the most
coral cover maintenance into the future. Differences between low, medium and high reef
clusters in cover timeseries are most notable under these two GCMs [@tbl-cluster-cid;
@fig-gcm-cover-trajectories]. Maintainance of coral cover into the future is linked to the
Equilibrium Climate Sensitivity of the GCM used as levels of future recovery and timespan of
cover maintainance increase as GCM ECS increases [@fig-gcm-cover-trajectories]. Under
high-ECS GCMs (GFDL-CM4, EC-Earth3-Veg and ACCESS-CM2) large declines and lower rates of
recovery in high cover clusters are common compared to lower-ECS GCMs.
